Anomaly_inspection

### 2021-02-13 New_Wages.Rmd
treat the observations with 0 rates per hour.
Update to survey year 2018 data.

@@

# load the downloaded data 
new_data_qnames <- read_rds(here::here("data-raw/wages-high-school-demo/data-frames/wages-high-school-demo-new_data_qnames.rds"))
categories_qnames <- read_rds(here::here("data-raw/wages-high-school-demo/data-frames/wages-high-school-demo-categories_qnames.rds"))

@@

# tidy the grade 
demog_education <- new_data_qnames %>%
  as_tibble() %>%
  select(CASEID_1979,
         starts_with("HGCREV"),
         "HGC_2012",
         "HGC_2014",
         "HGC_2016") %>%
  pivot_longer(!CASEID_1979,
               names_to = "var",
               values_to = "grade") %>%
  separate("var", c("var", "year"), sep = -4) %>%
  filter(!is.na(grade)) %>%
  select(-var)

@@

highest_year <- demog_education %>%
  group_by(CASEID_1979) %>%
  mutate(hgc_i = max(grade)) %>%
  filter(hgc_i == grade) %>%
  filter(year == first(year)) %>%
  rename(yr_hgc = year) %>%
  select(CASEID_1979, yr_hgc, hgc_i) %>%
  ungroup() %>%
  mutate('hgc' = ifelse(hgc_i == 0, "NONE",
                                  ifelse(hgc_i == 1, "1ST GRADE",
                                         ifelse(hgc_i == 2, "2ND GRADE",
                                                ifelse(hgc_i == 3, "3RD GRADE",
                                                       ifelse(hgc_i >= 4 & hgc_i <= 12, paste0(hgc_i,"TH GRADE"),
                                                              ifelse(hgc_i == 13, "1ST YEAR COL",
                                                                     ifelse(hgc_i == 14, "2ND YEAR COL",
                                                                            ifelse(hgc_i == 15, "3RD YEAR COL",
                                                                                   ifelse(hgc_i == 95, "UNGRADED", paste0((hgc_i - 12), "TH YEAR COL")))))))))))
```

@@

for(ayear in c(1979:1994, 1996, 1998, 2000, 2002, 2004, 2006, 2008, 2010, 
               2012, 2014, 2016)) {
   hours[[ayear]] <- get_hour(ayear)
}

@@

for(ayear in c(1979:1994, 1996, 1998, 2000, 2002, 2004, 2006, 2008, 2010, 
               2012, 2014, 2016)) {
   rates[[ayear]] <- get_rate(ayear)
}

@@

hours_wages <- left_join(rates_all, 
                         hours_all, 
                         by = c("id", "year", "job"))
```

>>>>

```{r}
#source(here::here("data-raw/NLSY79/NLSY79.R"))
```

Creates four files: new_data, has the variables using RNUM;
new_data_qnames, has the data with qnames
categories_vallabels, has RNUM and coding of each variable;
categories_qnames, has qname and coding of each variable;
(qname must be Question name?)

@@

# write_rds(as_tibble(new_data_qnames), 
#    here::here("data-raw/NLSY79/NLSY79-new_data_qnames.rds"),       
#       compress = "xz")

# write_rds(as_tibble(categories_qnames), 
#          here::here("data-raw/NLSY79/NLSY79-categories_qnames.rds"), 
#        compress = "xz")

# load the downloaded data 
new_data_qnames <- read_rds(here::here("data-raw/NLSY79/NLSY79-new_data_qnames.rds"))
categories_qnames <- read_rds(here::here("data-raw/NLSY79/NLSY79-categories_qnames.rds"))

@@

# tidy the grade 
demog_education <- new_data_qnames %>%
  as_tibble() %>%
  rename(HGC_2018 = `Q3-4_2018`) %>%
  select(CASEID_1979,
         starts_with("HGCREV"),
         "HGC_2012",
         "HGC_2014",
         "HGC_2016",
         "HGC_2018") %>%
  pivot_longer(!CASEID_1979,
               names_to = "var",
               values_to = "grade") %>%
  separate("var", c("var", "year"), sep = -4) %>%
  filter(!is.na(grade)) %>%
  select(-var)

@@

highest_year <- demog_education %>%
  group_by(CASEID_1979) %>%
  mutate(hgc_i = max(grade)) %>%
  filter(hgc_i == grade) %>%
  filter(year == first(year)) %>%
  rename(yr_hgc = year) %>%
  select(CASEID_1979, yr_hgc, hgc_i) %>%
  ungroup() %>%
  mutate('hgc' = ifelse(hgc_i == 0, "NONE",
                                  ifelse(hgc_i == 1, "1ST GRADE",
                                         ifelse(hgc_i == 2, "2ND GRADE",
                                                ifelse(hgc_i == 3, "3RD GRADE",
                                                       ifelse(hgc_i >= 4 & hgc_i <= 12, paste0(hgc_i,"TH GRADE"),
                                                              ifelse(hgc_i == 13, "1ST YEAR COL",
                                                                     ifelse(hgc_i == 14, "2ND YEAR COL",
                                                                            ifelse(hgc_i == 15, "3RD YEAR COL",
                                                                                   ifelse(hgc_i == 95, "UNGRADED", paste0((hgc_i - 12), "TH YEAR COL")))))))))))

@@

for(ayear in c(1979:1994, 1996, 1998, 2000, 2002, 2004, 2006, 2008, 2010, 
               2012, 2014, 2016, 2018)) {
   hours[[ayear]] <- get_hour(ayear)
}

@@

for(ayear in c(1979:1994, 1996, 1998, 2000, 2002, 2004, 2006, 2008, 2010, 
               2012, 2014, 2016, 2018)) {
   rates[[ayear]] <- get_rate(ayear)
}

@@

hours_wages <- left_join(rates_all, 
                         hours_all, 
                         by = c("id", "year", "job")) %>%

# set the 0 value in rate_per_hour as NA 
  mutate(rate_per_hour = ifelse(rate_per_hour == 0, NA,
                                rate_per_hour))
```

### 2021-02-13 School_drop_out.Rmd
Update to survey year 2018 data.

wages_do <- wages %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_hgc >= 19))
```

@@

wages_do_w <- wages_w %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_hgc >= 19))
```

@@

```{r}
wages_middle_w <- wages_w %>%
  filter(hgc %in% c("6TH GRADE", 
                    "7TH GRADE",
                    "8TH GRADE"))
```

>>>>

wages_do <- wages %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_hgc >= 19))

wages_do_comp <- wages_do %>%
  filter(gender == "MALE" &
           age_1979 %in% c(14, 15, 16, 17))
summary(wages_do_comp$mean_hourly_wage)
```

@@

wages_do_w <- wages_w %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_hgc >= 19))

wages_do_comp_w <- wages_do_w %>%
  filter(gender == "MALE" &
           age_1979 %in% c(14, 15, 16, 17))
summary(wages_do_comp_w$mean_hourly_wage)
```

@@

```{r}
wages_middle_w <- wages_w %>%
  filter(hgc %in% c("6TH GRADE", 
                    "7TH GRADE",
                    "8TH GRADE"))

```

### 2021-02-13 anomaly_v2.Rmd
Update to survey year 2018 data.

```{r data}
load("wages_hs2020.rda")
```

```{r wages}
wages <- as_tsibble(x = wages_hs2020,
                    key = id,
                    index = year,
                    regular = FALSE)
```

@@

### Plot the wages with low variance in their lm-residuals
```{r}
bottom12 <- wages_lm_var %>%
  filter(rank >= 5995) %>%
  left_join(wages, by = "id")

@@

```{r}
ggplot(wages) +
  geom_boxplot(aes(x = mean_hourly_wage)) +
  facet_wrap(~year)
```

>>>>

```{r data}
load("wages_hs2020_weighted_v2.rda")
```

```{r wages}
wages <- as_tsibble(x = wages_hs2020_weighted,
                    key = id,
                    index = year,
                    regular = FALSE)
```

@@

### Plot the wages with low variance in their lm-residuals
```{r}
bottom12 <- wages_lm_var %>%
  slice_tail(n =20) %>%
  left_join(wages, by = "id")

@@

### 2021-02-13 anomaly_v3.Rmd
Update to survey year 2018 data.

```{r data}
load("wages_hs2020_weighted_v2.rda")
```

@@

complete_year_obs <- wages_obs %>%
  filter(n_obs == 27) %>%
  left_join(wages_lm_var, by = "id") %>%
  arrange(desc(var))
```

>>>>

```{r data}
load("wages_hs2020_weighted_updated2018.rda")
```

@@

complete_year_obs <- wages_obs %>%
  filter(n_obs == 28) %>%
  left_join(wages_lm_var, by = "id") %>%
  arrange(desc(var))
```
